---
title: "Introduction to hoopr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to hoopr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(hoopR)
```

# hoopR

This vignette will help demonstrate the functions in the hoopR package. This will help introduce and demonstrate various ways to use the functions and how to interpret the results.

## Overview

The hoopR package deals with NBA data from basketball-reference.com. This is live data which is updated at the end of each season. The data revolves around the major awards which are given out at the end of each NBA season -- MVP (Most Valuable Player), DPOY (Defensive Player of the Year), ROY (Rookie of the Year), SMOY (Sixth Man of the Year),  and MIP (Most Improved Player). The purpose of this package is to demonstrate how the awards have changed over the years in terms of various statistics (Points, Rebounds, Assists, etc.), and this package can also show more specific things such as which player has won the most MVPs, or which DPOY has averaged the most blocks, or even which team has had the most ROYs. Some fun ways to use this package include quizzing your friends on their NBA knowledge or to support your claims in debates about certain players.

Important Features:
* awards - "MVP", "DPOY", "ROY", "MIP", "SMOY"
* stats - "PTS", "TRB", "AST", "STL", "BLK", "Age", "G", "MP", "FG%", "3P%", "FT%", "WS", "WS/48"

## Demonstrating Functions

### award_stat()
**award_stat()** will graph how an award has changed over time
Function Parameters include:
* award
* stat
* start
* end
* anim

```{r}
award_stat("MVP", "PTS", anim = F)
```

As you will see, the functions in hoopR require the specification of the award type in quotes. 

It appears that there are a lot of high point values before 1980. If we wanted to restrict the seasons to 1980 and after, we could run the code again, this time with **start = 1980**.

```{r}
award_stat("MVP", "PTS", start = 1980, anim = F)
```

We could also restrict the end season with (end = ) or we could choose to animate the graph with (anim = T).

### award_stats()
The **award_stats()** function closely resembles the previous function. However, in this function, we can specify multiple stats at a time. 

```{r}
award_stats("DPOY", c("BLK", "STL"), start = 2000, end = 2010)
```

Note how we specify our **stats** parameter in this function -- use c() and quote the stats we wish to compare. The graph above shows that from 2000 to 2010, the Defensive Player of the Year tends to average more blocks than steals, perhaps showing blocks as a high indicator of who will win the award.

### award()
The **award()** function determines which players have won the most of a certain award.

```{r}
award("MVP")
```

Perhaps we only want to find the 5 players who have won the most MVPs. We could do something like this below.

```{r, results = 'hide'}
award("MVP", top = 5)
```

### player_stats()
The **player_stats()** function shows which award winner had the most of a certain stat.

In the previous part, we saw that Kareem Abdul-Jabbar has won the most MVPs in NBA history, but which MVP has been the most impressive in terms of scoring output?

```{r}
player_stats("MVP", "PTS", top = 5)
```

From the output above, we can see that Wilt Chamberlain's 1960 season was the most impressive in terms of scoring at 37.6 points per game.

### awards()
The **awards()** function is a variation of the award() function. We can determine which players have won the most of multiple awards combined. 

For example, let's find out if Kareem still has the most awards when we combine both the MVP and DPOY award.

```{r}
awards(c("MVP", "DPOY"))
```


Now, Kareem and Michael Jordan are tied for 6 MVP + DPOY awards.
Note that specifying multiple awards is similar to specifying multiple stats as shown previously.

### add_stats()
The **add_stats()** function is another function in which we can combine multiple things together, similar to the awards() function. In add_stats(), we can choose multiple stats.
We previously saw that Wilt averaged the most points in an MVP season, but is he a well-rounded player? To determine this, let's combine points, rebounds, and assists for MVPs.

```{r}
add_stats("MVP", c("PTS", "TRB", "AST"), top = 5)
```

Even after combining stats, Wilt's 1960 MVP season is still the most impressive when it comes to stats, as he averaged almost 67 points+rebounds+assists per game!

### teams()
The **teams()** function compares teams. We have seen how this package can compare an award from season-to-season or from player-to-player. Now, teams() focuses on how awards are broken down by team.

For example, what if we wanted to determine which team has won the most Rookie of the Year awards.

```{r}
teams("ROY", top = 5)
```

From the output above, we can see that Portland has had the most Rookie of the Years with 4, perhaps indicating that they have a great drafting process.

We can also view this data in a graph.
```{r}
teams("ROY", top = 5, plot = T)
```

